\begin{center} \bf \sffamily \LARGE Prisoner's dilemma with stochastic payoffs\\[-1cm] \end{center}

### 2022-08-26 paper/pairwise_comparison_process_diagram.tex
working on the manuscript

    % %%%%% game stage %%%%%
    \node at (0, .7) (turns) {turn};

    \pic[BurntOrange] at (0, 0) (myman) {man};
    \node at (0, -.6) {B};
    \pic[RoyalBlue] at (0, -2) (myman) {man};
    \node at (0, -2.6) {F};

    \coordinate (B) at (0.5, -.6);
    \coordinate (F) at (0.5, -2.6);

    \node at (1.5, .7) (turn1) {1};
    \node[circle, inner sep=1pt, outer sep=1pt, draw, fill] at (1.5, 1.7) (exit) {};
    \node[circle, draw] (C) at (1.5, -.6)  {$C$};
    \node[circle, draw] (D) at (1.5, -2.6) {$D$};

    \draw (B) edge[out=0, in=180, ->, thick] node [above] {$y_{B}$} (C);
    \draw (F) edge[out=0, in=180, ->, thick] node [above] {$y_{F}$} (D);

    \node at (3, .7) (turn2) {2};
    \node[circle, inner sep=1pt, outer sep=1pt, draw, fill] at (3, 1.7) (exit2) {};
    \node[circle, draw] (C2)at (3, -.6)  {$C$};
    \node[circle, draw] (D2) at (3, -2.6) {$D$};

    \draw (C) edge[out=0, in=180, ->, thick] node [above] {$q_{B}$} (C2);
    \draw (D) edge[out=0, in=180, ->, thick] node [above] {$p_{F}$} (D2);

    \draw (turn1) edge[out=15, in=165, ->, thick] node [above] {$\delta$} (turn2);
    \draw (turn1) edge[out=90, in=-90, ->, thick] node [above, rotate=90] {$1 - \delta$} (exit);
    \draw (turn2) edge[out=90, in=-90, ->, thick] node [above right] {$1 - \delta$} (exit2);

    \node[circle] at (4, -.6) {$\dots$};
    \node[circle] at (4, -2.6) {$\dots$};

>>>>

    \node at (0, 0) {\includestandalone{population}};
    \draw[thick] (2.5, 3) -- (2.5, -2);

    \node at (3.5, 2.5) {B)};
    \node at (5, 2) {\includestandalone[width=.13\textwidth]{mutation}};

    \node at (3, -.7) {D)};
    \node at (5, -1) {\includestandalone[width=.25\textwidth]{updating}};

    \node at (8.4, 2.5) {C)};
    \node at (10, .5) {\includestandalone[width=.25\textwidth]{game_stage}};

    \draw[thick] (7.7, 3) -- (7.7, -2);
